RDF Validation Requirements - Evaluation and Logical Underpinning

### 2015-01-06 paper/RDF validation requirements/RDF validation requirements.tex
add descriptions

\begin{itemize}
	\item R-61-SYMMETRIC-OBJECT-PROPERTIES
\end{itemize}

\begin{itemize}
	\item A role is symmetric if it is equivalent to its own inverse \cite{Kroetzsch2012}
  \item An object property symmetry axiom SymmetricObjectProperty( OPE ) states that the object property expression OPE is symmetric — that is, if an individual x is connected by OPE to an individual y, then y is also connected by OPE to x. 	
\end{itemize}

@@

\subsubsection{Asymmetric Object Properties}

\begin{itemize}
	\item R-62-ASYMMETRIC-OBJECT-PROPERTIES
\end{itemize}

\begin{itemize}
	\item A role is asymmetric if it is disjoint from its own inverse \cite{Kroetzsch2012}
	\item An object property asymmetry axiom AsymmetricObjectProperty( OPE ) states that the object property expression OPE is asymmetric — that is, if an individual x is connected by OPE to an individual y, then y cannot be connected by OPE to x. 
\end{itemize}

>>>>

\ms{Symmetric Object Properties} corresponds to the requirement \\
\ms{R-61-SYMMETRIC-OBJECT-PROPERTIES}.
A role is symmetric if it is equivalent to its own inverse \cite{Kroetzsch2012}.
An object property symmetry axiom states that the object property expression OPE is symmetric - that is, if an individual x is connected by OPE to an individual y, then y is also connected by OPE to x.

The property \ms{marriedTo} is symmetric:

@@

\section{Asymmetric Object Properties}

\ms{Asymmetric Object Properties} corresponds to the requirement \\
\ms{R-62-ASYMMETRIC-OBJECT-PROPERTIES}.
A role is asymmetric if it is disjoint from its own inverse \cite{Kroetzsch2012}.
An object property asymmetry axiom AsymmetricObjectProperty( OPE ) states that the object property expression OPE is asymmetric - that is, if an individual x is connected by OPE to an individual y, then y cannot be connected by OPE to x.
